### 2024-08-07 manuscript.tex
Multiple updates and additions

@@

@@

@@

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available at from NASA
NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
openly available from Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}).  The other voyage and station data
are openly available on Zenodo (). Subsetted model and reanalysis data for the
voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().

>>>>

\subsection{CERES}

TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
Energy System (CERES) instruments on board of the Terra and Aqua satellites
\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
clouds 1 degree daily edition 4A product
(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
\citep{doelling2013,doelling2016}.

@@

\subsection{Data processing}

The radiation calculations were done in such a way that they always represent
averages of daily means. This is done in order to be consistent with the CERES
SYN1deg data, which are expressed as daily means. Therefore, for every
instantaneous profile in the simulated lidar data is assigned a daily mean
radiation value corresonding to theo the day (in UTC). In turn, the average
radiation during the entire voyage or station measurement is calculated as the
average of the profile values. In the observed lidar data, the daily mean
radiation value is taken from the spatially and temporally co-located CERES
SYN1deg data for the day (in UTC). The voyage or station measurement average
is calculated in the same way.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/clt_hist.pdf}
\caption{
Daily total cloud fraction histograms calculated as the average of all voyage
and station histograms. The models and subsets are as in Fig.
\ref{fig:cloud-occurrence}
}
\label{fig:clt-hist}
\end{figure}

@@

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available at from NASA
NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
openly available from Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The CERES products are available
from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA
Atmospheric Science Data Centre
(\url{https://asdc.larc.nasa.gov/project/CERES}).  The other voyage and station
data are openly available on Zenodo (). Subsetted model and reanalysis data for
the voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().
